---
title: "Flow charts for methods and modelling steps"
author: "Marie Delalay"
date: ''
output:
  pdf_document:
    toc: yes
  html_document:
    df_print: kable
    fig_caption: yes
    highlight: zenburn
    number_sections: yes
    toc: yes
  word_document:
    toc: yes
---

FIRST: READ THE LINES BELOW UNTIL THE FIRST TITLE.

This file contains flow charts of modelling steps and methods.

Here are instructions on how to knit this file:

- **your_absolute_path** must be changed in the chunk below
- knit this file to to html


```{r, include = FALSE}
#shell.exec("http://rich-iannone.github.io/DiagrammeR/graphviz_and_mermaid.html#graphviz")
rm(list=ls())

#### Set seed and options ####
set.seed(1)
options("scipen"=3, "digits"=6) #; ?options

#### Libraries ####
x <- c("DiagrammeR","DiagrammeRsvg")
y <- which(!x %in% rownames (installed.packages()))
if (length(y) >0) {install.packages(x[y])}
lapply(x, library, character.only = TRUE)

#### Knit options ####
knitr::opts_chunk$set(echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, results="asis", fig.cap = "", include = TRUE) # For more on chunk options, see: https://yihui.name/knitr/options/

absolute_path <- "C:/Users/mdela/Dropbox/Prof/NUS/Projects/Modelling/Model"  # **your-abslolute_path**

#Function to save as .snv (thanks to Kevin Mader)
WRITE_AS_SVG <-function(in_graph, out_name = "test.svg") {
  out_svg<-file(out_name, "w")
  writeLines(DiagrammeRsvg::export_svg(in_graph), out_svg)
  close(out_svg)
  print(paste0(out_name, " in folder"))
}
```

# Template

Results of the template are hidden. 

```{r, results="hide"}

name_xxx_empty <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] data not present in previous stages / response in general
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [2] data present in next stage / final output
        node [color = orange, shape = triangle, style = filled, fillcolor= OldLace, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [3] operations  / conditions or questions                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [7] data from previous stages  / response in model
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same; 'xxx'
        }
        
        # [5] edges      
        subgraph cluster { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        }
        
        }
        
        ")

name_xxx_empty

#WRITE_AS_SVG(name_xxx_empty,"nice.svg")
```

# Modelling steps of the vulnerability and damage papers

## Overview flow model

```{r}
name_010 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Overview flow model
        'Flow1 and Flow2: flood raster (i in [1,I])';
        'Flow3: possible toe raster (i in [1,I])';
        'output of hazard module'        
        'Flow4: HPP value raster (k in [1,K]) ';
        'Flow4: road value raster ';
        'Flow4: settlement value raster (k in [1,K]) ';
        'Flow4: farmland value raster';
        'output of asset module';
        'Flow6: sampled landslides and hazard rasters';
        'Flow7 to Flow10: PAE and sampled MDD';
        'Distribution of direct and ind. damages'   
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## aggregation module        
        'Monte-Carlo simulations (j in [1,J])'

        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        'I. hazard module'
        'II. asset module'
        'III. aggregation module'
        
        # [4] sort or separate
        subgraph {
        rank = same; 
        }
        
        # [5] edges      
        subgraph cluster_11 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'I. hazard module' -> {'Flow1 and Flow2: flood raster (i in [1,I])' 'Flow3: possible toe raster (i in [1,I])'}
        {'Flow1 and Flow2: flood raster (i in [1,I])' 'Flow3: possible toe raster (i in [1,I])'} -> 'output of hazard module'
        }
        
        # [5] edges      
        subgraph cluster_12 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'II. asset module' -> {'Flow4: HPP value raster (k in [1,K]) ' 'Flow4: road value raster ''Flow4: settlement value raster (k in [1,K]) ''Flow4: farmland value raster'}
        {'Flow4: HPP value raster (k in [1,K]) ' 'Flow4: road value raster ''Flow4: settlement value raster (k in [1,K]) ''Flow4: farmland value raster'} -> 'output of asset module'
        }
        
        # [5] edges      
        subgraph cluster_13 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'output of asset module' 'output of hazard module'} -> 'III. aggregation module'
        'III. aggregation module' -> 'Monte-Carlo simulations (j in [1,J])'
        {'Monte-Carlo simulations (j in [1,J])'} -> {'Flow6: sampled landslides and hazard rasters' 'Flow7 to Flow10: PAE and sampled MDD'}
        {'Flow6: sampled landslides and hazard rasters' 'Flow7 to Flow10: PAE and sampled MDD'} -> 'Distribution of direct and ind. damages'
        }
        
        }
        ")

name_010
```


## (01) - Hazard module: Floods, data preparation

```{r}
name_020 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, data preparation        
        'unfilled DEM raster';
        'polygon of watershed with outlet at Dolalghat';  
        'results of DEM validation';
        'DEM raster';
        'boolean river raster';
        'slope raster';
        'polygon of study area';
        'river reach ID raster';
        'river reach ID buffer raster';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, data preparation        
        'ArcGIS analysis'; 
        'elevation RMSE';
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, data preparation
        'SRTM 1 arc-sec rasters'; 'ASTER 1 arc-sec rasters';
        'GPS measurements';
        'polygon of Nepal by district';
        
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same;
        }
        
        # [5] edges
        subgraph cluster_21 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'SRTM 1 arc-sec rasters' 'ASTER 1 arc-sec rasters'} ->'unfilled DEM raster'
        'unfilled DEM raster' 
        }
        
        # [5] edges
        subgraph cluster_22 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        #1.5
        'unfilled DEM raster' -> 'ArcGIS analysis'
        'ArcGIS analysis' -> {'polygon of watershed with outlet at Dolalghat' 'DEM raster' 'boolean river raster' 'slope raster' 'river reach ID buffer raster'}
        {'polygon of watershed with outlet at Dolalghat' 'polygon of Nepal by district'} -> 'polygon of study area'
        }
        
        # [5] edges
        subgraph cluster_23 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'DEM raster' 'GPS measurements'} -> 'elevation RMSE' 
        'elevation RMSE' -> 'results of DEM validation'
        }
        
        # [5] edges
        subgraph cluster_24 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'river reach ID buffer raster' 'boolean river raster'} -> 'river reach ID raster'
        }
        
        }
        ")

name_020
```

## (02) - Hazard module: Floods, flood raster

```{r}
name_030 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, flood raster
        'i-th flood raster';  
        'i-th initial water stages by river reach'; 
        'results of validation of initial water stages';
        'initial water stage raster'; 
        'DEM raster';
        'river reach ID raster'
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, flood raster
        'distribution fitting'; 
        'quantile derivation'; 
        'dependencies of initial water stages'; 
        '(if DHM data available)';
        '(if DHM data not available)'; 
        'RMSE of initial water stage' 'flood function';
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, flood raster
        'empirical 99%-quantile of water stage (1)'; 
        'empirical 99%-quantile of water stage (2)';
        'DHM data: water discharge and water stage';
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same; 
        }
        
        # [5] edges
        subgraph cluster_31 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        '(if DHM data available)' -> 'DHM data: water discharge and water stage'
        '(if DHM data not available)'-> 'empirical 99%-quantile of water stage (1)'
        {'DHM data: water discharge and water stage' 'empirical 99%-quantile of water stage (1)'}-> 'distribution fitting'
        'distribution fitting' -> 'quantile derivation'
        {'quantile derivation' 'dependencies of initial water stages'} -> 'i-th initial water stages by river reach'
        }
        
        # [5] edges 
        subgraph cluster_32 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'i-th initial water stages by river reach' 'empirical 99%-quantile of water stage (2)'} -> 'RMSE of initial water stage' -> 'results of validation of initial water stages'
        }
        
        # [5] edges
        subgraph cluster_33 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'river reach ID raster' 'i-th initial water stages by river reach'} -> 'initial water stage raster'
        {'initial water stage raster' 'DEM raster'} -> 'flood function' -> 'i-th flood raster'
        }
        
        }
        ")

name_030
```

## (03) - Hazard module: raster of possible landslides

```{r}
name_040 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: raster of possible landslides
        'slope raster' 
        'boolean slope >30% raster'; 
        'orientation at flood curve raster'; 
        'rock weight raster'; 
        'angle at flood curve raster'; 
        'angle weight raster'; 
        'toe orientation raster'; 
        'toe weight raster' ;
        'average size of landslides'; 
        'j-th ratio of landslide count'; 
        'boolean river raster';
        'polygon riparian areas';
        'i-th possible toe raster'
        'i-th flood raster'
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'select flooded toes';
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: raster of possible landslides
        'data on rocks and geology'; 
        'polygons of geological formations';  
        'data on weights given angle'; 
        'landslide history data';
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same; 
        }
        
        # [5] edges
        subgraph cluster_41 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'slope raster' -> 'boolean slope >30% raster'
        'boolean river raster' -> 'orientation at flood curve raster'
        {'boolean slope >30% raster' 'orientation at flood curve raster'}  -> 'toe orientation raster'
        }
        
        # [5] edges
        subgraph cluster_42 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'data on rocks and geology' 'polygons of geological formations'} -> 'rock weight raster'   
        {'boolean river raster' 'orientation at flood curve raster'} -> 'angle at flood curve raster' 
        {'angle at flood curve raster' 'data on weights given angle'} -> 'angle weight raster' 
        {'angle weight raster' 'rock weight raster'} -> 'toe weight raster' 
        }
        
        # [5] edges
        subgraph cluster_43 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'landslide history data' -> 'average size of landslides'
        'boolean river raster'  -> 'polygon riparian areas'
        {'landslide history data' 'polygon riparian areas'} -> 'j-th ratio of landslide count'
        }

        # [5] edges
        subgraph cluster_44 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'toe orientation raster' 'i-th flood raster'} -> 'select flooded toes' 
        'select flooded toes' -> 'i-th possible toe raster'
        }

        }
        ")
name_040

```

## (04) - Asset module: value rasters

```{r}
name_050 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Asset module: value rasters
        'k-th HPP asset raster' 
        'k-th HPP revenue raster' 
        'road asset raster' 
        'LULC raster' 
        'boolean settlement raster' 
        'boolean farmland raster' 
        'k-th settlement asset raster' 
        'farmland asset raster';
        'k-th points of HW and PH locations'

        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Asset module: value rasters
        'polygons of HPPs lease areas' 
        'data on location of HW and PH' 
        'data on unit cost per MW' 
        'data on maximum revenue per MW' 
        'boolean road raster' 
        'data on unit cost per km' 
        'Sentinel data' 
        'data on unit cost and HH density' 
        'data on farm gate price and crop type';
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]

        # [4] sort or separate
        subgraph {
        rank = same; 
        }        
        

        # [5] edges
        subgraph cluster_52 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'polygons of HPPs lease areas' 'data on location of HW and PH'} -> 'k-th points of HW and PH locations'
        {'data on unit cost per MW'  'k-th points of HW and PH locations'} -> 'k-th HPP asset raster'
        }
        
        # [5] edges
        subgraph cluster_52 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'data on maximum revenue per MW' 'k-th points of HW and PH locations'} -> 'k-th HPP revenue raster'
        }
        
        # [5] edges
        subgraph cluster_53 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'data on unit cost per km' 'boolean road raster'} -> 'road asset raster'
        }
        
        # [5] edges
        subgraph cluster_54 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'Sentinel data' -> 'LULC raster'
        'LULC raster' -> 'boolean settlement raster'
        {'boolean settlement raster' 'data on unit cost and HH density'} -> 'k-th settlement asset raster'
        }
        
        # [5] edges
        subgraph cluster_54 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'LULC raster' -> 'boolean farmland raster' #15
        {'boolean farmland raster' 'data on farm gate price and crop type'} -> 'farmland asset raster'
        }
        
        }
        ")

name_050

```

## (05) - Aggregation module: PAE and MDD

```{r}

name_060 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module: PAE and MDD
        'HPP PAE';
        'road PAE'; 
        'settlement PAE';
        'farmland PAE'; '(i*j*k)-th HPP MDD';
        '(i*j)-th road MDD';
        '(i*j*k)-th settlement MDD';
        '(i*j)-th farmland MDD';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module: PAE and MDD        
        'set deterministic PAE';
        'parameterise stochastic MDD';
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module: PAE and MDD        
        'asset valuation data';
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same; 
        }         
        
        # [5] edges
        subgraph cluster_61 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'asset valuation data'
        }
        
        # [5] edges
        subgraph cluster_62 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'asset valuation data' -> 'set deterministic PAE' 
        'set deterministic PAE' -> {'HPP PAE' 'road PAE' 'settlement PAE' 'farmland PAE'}
        }
        
        # [5] edges 
        subgraph cluster_63 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'asset valuation data' -> 'parameterise stochastic MDD'
        'parameterise stochastic MDD' -> {'(i*j*k)-th HPP MDD' '(i*j)-th road MDD' '(i*j*k)-th settlement MDD' '(i*j)-th farmland MDD'}
        }        
        
        }
        ")

name_060

```

## (06) - Aggregation module: hazard rasters

```{r}

name_070 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module: hazard rasters
        'i-th possible toe raster'; 
        '(i*j)-th actual landslide raster'; 
        'i-th flood raster'; 
        'j-th ratio of landslide count'; 
        'toe weight raster'; 
        'average size of landslides'; 
        '(i*j)-th hazard raster';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module: hazard rasters
        'build-landslide function';
        'join hazards';
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same; 
        }
        
        # [5] edges      
        subgraph cluster_71 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'j-th ratio of landslide count' 'i-th possible toe raster' 'toe weight raster' 'average size of landslides'} -> 'build-landslide function' 
        'build-landslide function' -> '(i*j)-th actual landslide raster'
        {'i-th flood raster''(i*j)-th actual landslide raster'} -> 'join hazards' 
        'join hazards' -> '(i*j)-th hazard raster' 
        }
        
        }
        ")

name_070

```

## (07) - Aggregation module - HPP

```{r}
name_080 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module - HPP
        '(i*j)-th hazard raster';
        'k-th HPP asset raster';
        '(i*j*k)-th HPP exposure raster';
        '(i*j*k)-th HPP damaged exposure raster'; 
        '(i*j*k)-th direct damages to HPP'; 
        '(i*j*k)-th indirect damages to HPP';
        'HPP PAE';
        'k-th HPP revenue raster';
        '(i*j*k)-th HPP MDD';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        # Aggregation module - HPP
        'subset and conditional on MDD'
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph cluster_82 {
        rank = same; '(i*j*k)-th indirect damages to HPP' '(i*j*k)-th direct damages to HPP'
        }
        
        # [5] edges
        subgraph cluster_81 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'k-th HPP asset raster' '(i*j)-th hazard raster'} -> '(i*j*k)-th HPP exposure raster'
        {'HPP PAE' '(i*j*k)-th HPP exposure raster'} -> '(i*j*k)-th HPP damaged exposure raster'
        {'(i*j*k)-th HPP MDD' '(i*j*k)-th HPP damaged exposure raster'} -> '(i*j*k)-th direct damages to HPP'
        {'(i*j*k)-th HPP MDD' '(i*j*k)-th HPP damaged exposure raster' 'k-th HPP revenue raster'} -> 'subset and conditional on MDD' 
        'subset and conditional on MDD' -> '(i*j*k)-th indirect damages to HPP' 
        }
        
        }
        ")

name_080
```

## (08) - Aggregation module - road


```{r}
name_090 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module - road
        '(i*j)-th hazard raster';
        '(i*j)-th road exposure raster'; 
        '(i*j)-th road damaged exposure raster';
        '(i*j)-th mean road MDD';
        '(i*j)-th direct damages to road'; 
        '(i*j)-th indirect damages to road';
        'road asset raster';
        'road PAE';
        '(i*j)-th road MDD';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'data on (1) duration road closure and (2) customs revenues';        


        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph cluster_91 {
        rank = same; '(i*j)-th indirect damages to road' '(i*j)-th direct damages to road'
        }
        
        # [5] edges
        subgraph cluster_92 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'road asset raster' '(i*j)-th hazard raster'} -> '(i*j)-th road exposure raster' # 17b
        {'road PAE' '(i*j)-th road exposure raster'} -> '(i*j)-th road damaged exposure raster'  #17b
        {'(i*j)-th road MDD' '(i*j)-th road damaged exposure raster'} -> '(i*j)-th direct damages to road' #17b
        {'(i*j)-th road MDD'} -> '(i*j)-th mean road MDD' #17b
        {'(i*j)-th mean road MDD' 'data on (1) duration road closure and (2) customs revenues'} -> '(i*j)-th indirect damages to road' # 17b
        }
        
        }
        ")

name_090
```

## (09) - Aggregation module - settlement
```{r}
name_100 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module - settlement
        '(i*j)-th hazard raster'        
        '(i*j*k)-th settlement exposure raster';  
        '(i*j*k)-th settlement damaged exposure raster';
        '(i*j*k)-th direct damages to settlement'; 
        '(i*j)-th indirect damages to settlement';
        'k-th settlement asset raster';
        'settlement PAE';
        '(i*j)-th mean road MDD';
        '(i*j*k)-th settlement MDD'
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'data on road-related income';        

        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph cluster_101 {
        rank = same; '(i*j*k)-th direct damages to settlement' '(i*j)-th indirect damages to settlement';
        }
        
        # [5] edges
        subgraph cluster_102 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'k-th settlement asset raster' '(i*j)-th hazard raster'} -> '(i*j*k)-th settlement exposure raster' # 17b
        {'settlement PAE' '(i*j*k)-th settlement exposure raster'} -> '(i*j*k)-th settlement damaged exposure raster'  #17b
        {'(i*j*k)-th settlement MDD' '(i*j*k)-th settlement damaged exposure raster'} -> '(i*j*k)-th direct damages to settlement' #17b
        {'(i*j)-th mean road MDD' 'data on road-related income'} -> '(i*j)-th indirect damages to settlement' # 17b
        }
        
        }
        ")

name_100
```


## (10) - Aggregation module - farmland
```{r}
name_110 <- 
grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
      
      # [1] intermediary data / output data
      node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
      ## Aggregation module - farmland
      '(i*j)-th hazard raster'        
      '(i*j)-th farmland exposure raster';  
      '(i*j)-th farmland damaged exposure raster';
      '(i*j)-th direct damages to farmland';
      'farmland asset raster';
      '(i*j)-th hazard raster';
      'farmland PAE';
      '(i*j)-th farmland MDD';
      
      # [3] operations                
      node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
      
      # [7] input data
      node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
      
      # [6] title names
      node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
      
      # [4] sort or separate
      subgraph cluster_111 {
      rank = same; '(i*j)-th direct damages to farmland'
      }
      
      # [5] edges
      subgraph cluster_112 {
      edge [color = grey, arrowhead = vee, arrowtail = none]
      {'farmland asset raster' '(i*j)-th hazard raster'} -> '(i*j)-th farmland exposure raster' 
      {'farmland PAE' '(i*j)-th farmland exposure raster'} -> '(i*j)-th farmland damaged exposure raster' 
      {'(i*j)-th farmland MDD' '(i*j)-th farmland damaged exposure raster'} -> '(i*j)-th direct damages to farmland'
      }
      
      }
      ")

name_110
```

## Vulnerability
```{r}
name_120 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Vulnerability
        'settlement VDC ID raster'; 
        'i-th settlement vulnerability raster';
        'farmland VDC ID raster'; 
        'i-th farmland vulnerability raster';
        'boolean settlement raster'; 
        'boolean farmland raster';
        'i-th count of household and population at risk of flood'; 
        'i-th flood risk hotspots for settlement by VDC'; 
        'i-th flood risk hotspots for farmland by VDC';
        'LULC raster'
        'i-th flood raster';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Vulnerability       
        'intersect rasters for settlement'
        'intersect rasters for farmland'
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Vulnerability
        'VDC ID raster';
        'data on HH count and population count'
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph cluster_121 {
        rank = same; 'i-th count of household and population at risk of flood' 'i-th flood risk hotspots for settlement by VDC' 'i-th flood risk hotspots for farmland by VDC'
        }
        
        # [5] edges      
        subgraph cluster_124 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'LULC raster'
        'VDC ID raster'
        'i-th flood raster'
        }
        
        # [5] edges
        subgraph cluster_122 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'LULC raster'-> 'boolean settlement raster'
        {'boolean settlement raster' 'VDC ID raster'} -> 'settlement VDC ID raster'
        {'settlement VDC ID raster' 'i-th flood raster'} -> 'intersect rasters for settlement'
        'intersect rasters for settlement' -> 'i-th settlement vulnerability raster'
        {'i-th settlement vulnerability raster' 'data on HH count and population count'} -> 'i-th count of household and population at risk of flood'
        'i-th settlement vulnerability raster' -> 'i-th flood risk hotspots for settlement by VDC'
        }
        
        # [5] edges
        subgraph cluster_123 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'LULC raster'-> 'boolean farmland raster'
        {'boolean farmland raster' 'VDC ID raster'} -> 'farmland VDC ID raster'
        {'farmland VDC ID raster' 'i-th flood raster'} -> 'intersect rasters for farmland'
        'intersect rasters for farmland' -> 'i-th farmland vulnerability raster'
        'i-th farmland vulnerability raster' -> 'i-th flood risk hotspots for farmland by VDC'
        }
        
        }
        ")

name_120
```

## Consolidated modules - all

```{r, results="asis"}

name_1000 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]

#--------------------------------------- 
       
        # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, data preparation        
        'unfilled DEM raster';
        'polygon of watershed with outlet at Dolalghat';  
        'results of DEM validation';
        'DEM raster';
        'boolean river raster';
        'slope raster';
        'polygon of study area';
        'river reach ID raster';
        'river reach ID buffer raster';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, data preparation        
        'ArcGIS analysis'; 
        'elevation RMSE';
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, data preparation
        'SRTM 1 arc-sec rasters'; 'ASTER 1 arc-sec rasters';
        'GPS measurements';
        'polygon of Nepal by district';
        
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same;
        }
        
        # [5] edges
        subgraph cluster_20 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'SRTM 1 arc-sec rasters' 'ASTER 1 arc-sec rasters'} ->'unfilled DEM raster'
        'unfilled DEM raster' 
        }
        
        # [5] edges
        subgraph cluster_20 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        #1.5
        'unfilled DEM raster' -> 'ArcGIS analysis'
        'ArcGIS analysis' -> {'polygon of watershed with outlet at Dolalghat' 'DEM raster' 'boolean river raster' 'slope raster' 'river reach ID buffer raster'}
        {'polygon of watershed with outlet at Dolalghat' 'polygon of Nepal by district'} -> 'polygon of study area'
        }
        
        # [5] edges
        subgraph cluster_20 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'DEM raster' 'GPS measurements'} -> 'elevation RMSE' 
        'elevation RMSE' -> 'results of DEM validation'
        }
        
        # [5] edges
        subgraph cluster_20 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'river reach ID buffer raster' 'boolean river raster'} -> 'river reach ID raster'
        }
        
#------------------------------

 # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, flood raster
        'i-th flood raster';  
        'i-th initial water stages by river reach'; 
        'results of validation of initial water stages';
        'initial water stage raster'; 
        'DEM raster';
        'river reach ID raster'
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, flood raster
        'distribution fitting'; 
        'quantile derivation'; 
        'dependencies of initial water stages'; 
        '(if DHM data available)';
        '(if DHM data not available)'; 
        'RMSE of initial water stage' 'flood function';
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, flood raster
        'empirical 99%-quantile of water stage (1)'; 
        'empirical 99%-quantile of water stage (2)';
        'DHM data: water discharge and water stage';
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same; 
        }
        
        # [5] edges
        subgraph cluster_30 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        '(if DHM data available)' -> 'DHM data: water discharge and water stage'
        '(if DHM data not available)'-> 'empirical 99%-quantile of water stage (1)'
        {'DHM data: water discharge and water stage' 'empirical 99%-quantile of water stage (1)'}-> 'distribution fitting'
        'distribution fitting' -> 'quantile derivation'
        {'quantile derivation' 'dependencies of initial water stages'} -> 'i-th initial water stages by river reach'
        }
        
        # [5] edges 
        subgraph cluster_30 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'i-th initial water stages by river reach' 'empirical 99%-quantile of water stage (2)'} -> 'RMSE of initial water stage' -> 'results of validation of initial water stages'
        }
        
        # [5] edges
        subgraph cluster_30 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'river reach ID raster' 'i-th initial water stages by river reach'} -> 'initial water stage raster'
        {'initial water stage raster' 'DEM raster'} -> 'flood function' -> 'i-th flood raster'
        }

#------------------------------

   # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: raster of possible landslides
        'slope raster' 
        'boolean slope >30% raster'; 
        'orientation at flood curve raster'; 
        'rock weight raster'; 
        'angle at flood curve raster'; 
        'angle weight raster'; 
        'toe orientation raster'; 
        'toe weight raster' ;
        'average size of landslides'; 
        'j-th ratio of landslide count'; 
        'boolean river raster';
        'polygon riparian areas';
        'i-th possible toe raster'
        'i-th flood raster'
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'select flooded toes';
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: raster of possible landslides
        'data on rocks and geology'; 
        'polygons of geological formations';  
        'data on weights given angle'; 
        'landslide history data';
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same; 
        }
        
        # [5] edges
        subgraph cluster_40 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'slope raster' -> 'boolean slope >30% raster'
        'boolean river raster' -> 'orientation at flood curve raster'
        {'boolean slope >30% raster' 'orientation at flood curve raster'}  -> 'toe orientation raster'
        }
        
        # [5] edges
        subgraph cluster_40 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'data on rocks and geology' 'polygons of geological formations'} -> 'rock weight raster'   
        {'boolean river raster' 'orientation at flood curve raster'} -> 'angle at flood curve raster' 
        {'angle at flood curve raster' 'data on weights given angle'} -> 'angle weight raster' 
        {'angle weight raster' 'rock weight raster'} -> 'toe weight raster' 
        }
        
        # [5] edges
        subgraph cluster_40 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'landslide history data' -> 'average size of landslides'
        'boolean river raster'  -> 'polygon riparian areas'
        {'landslide history data' 'polygon riparian areas'} -> 'j-th ratio of landslide count'
        }

        # [5] edges
        subgraph cluster_40 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'toe orientation raster' 'i-th flood raster'} -> 'select flooded toes' 
        'select flooded toes' -> 'i-th possible toe raster'
        }


#--------------------------------

     # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Asset module: value rasters
        'k-th HPP asset raster' 
        'k-th HPP revenue raster' 
        'road asset raster' 
        'LULC raster' 
        'boolean settlement raster' 
        'boolean farmland raster' 
        'k-th settlement asset raster' 
        'farmland asset raster';
        'k-th points of HW and PH locations'
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Asset module: value rasters
        'polygons of HPPs lease areas' 
        'data on location of HW and PH' 
        'data on unit cost per MW' 
        'data on maximum revenue per MW' 
        'boolean road raster' 
        'data on unit cost per km' 
        'Sentinel data' 
        'data on unit cost and HH density' 
        'data on farm gate price and crop type';
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]

        # [4] sort or separate
        subgraph {
        rank = same; 
        }        
        

        # [5] edges
        subgraph cluster_50 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'polygons of HPPs lease areas' 'data on location of HW and PH'} -> 'k-th points of HW and PH locations'
        {'data on unit cost per MW'  'k-th points of HW and PH locations'} -> 'k-th HPP asset raster'
        }
        
        # [5] edges
        subgraph cluster_50 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'data on maximum revenue per MW' 'k-th points of HW and PH locations'} -> 'k-th HPP revenue raster'
        }
        
        # [5] edges
        subgraph cluster_50 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'data on unit cost per km' 'boolean road raster'} -> 'road asset raster'
        }
        
        # [5] edges
        subgraph cluster_50 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'Sentinel data' -> 'LULC raster'
        'LULC raster' -> 'boolean settlement raster'
        {'boolean settlement raster' 'data on unit cost and HH density'} -> 'k-th settlement asset raster'
        'k-th settlement asset raster'
        }
        
        # [5] edges
        subgraph cluster_50 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'LULC raster' -> 'boolean farmland raster' #15
        {'boolean farmland raster' 'data on farm gate price and crop type'} -> 'farmland asset raster'
        'farmland asset raster'
        }

#------------------------

  # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module: PAE and MDD
        'HPP PAE';
        'road PAE'; 
        'settlement PAE';
        'farmland PAE'; '(i*j*k)-th HPP MDD';
        '(i*j)-th road MDD';
        '(i*j*k)-th settlement MDD';
        '(i*j)-th farmland MDD';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module: PAE and MDD        
        'set deterministic PAE';
        'parameterise stochastic MDD';
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module: PAE and MDD        
        'asset valuation data';
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same; 
        }         
        
        # [5] edges
        subgraph cluster_60 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'asset valuation data'
        }
        
        # [5] edges
        subgraph cluster_60 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'asset valuation data' -> 'set deterministic PAE' 
        'set deterministic PAE' -> {'HPP PAE' 'road PAE' 'settlement PAE' 'farmland PAE'}
        }
        
        # [5] edges 
        subgraph cluster_60 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'asset valuation data' -> 'parameterise stochastic MDD'
        'parameterise stochastic MDD' -> {'(i*j*k)-th HPP MDD' '(i*j)-th road MDD' '(i*j*k)-th settlement MDD' '(i*j)-th farmland MDD'}
        }      

#---------------------

  # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module: hazard rasters
        'i-th possible toe raster'; 
        '(i*j)-th actual landslide raster'; 
        'i-th flood raster'; 
        'j-th ratio of landslide count'; 
        'toe weight raster'; 
        'average size of landslides'; 
        '(i*j)-th hazard raster';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module: hazard rasters
        'build-landslide function';
        'join hazards';
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same; 
        }
        
        # [5] edges      
        subgraph cluster_70 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'j-th ratio of landslide count' 'i-th possible toe raster' 'toe weight raster' 'average size of landslides'} -> 'build-landslide function' 
        'build-landslide function' -> '(i*j)-th actual landslide raster'
        {'i-th flood raster''(i*j)-th actual landslide raster'} -> 'join hazards' 
        'join hazards' -> '(i*j)-th hazard raster' 
        }
        
#------------------------------

 # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module - HPP
        '(i*j)-th hazard raster';
        'k-th HPP asset raster';
        '(i*j*k)-th HPP exposure raster';
        '(i*j*k)-th HPP damaged exposure raster'; 
        '(i*j*k)-th direct damages to HPP'; 
        '(i*j*k)-th indirect damages to HPP';
        'HPP PAE';
        'k-th HPP revenue raster';
        '(i*j*k)-th HPP MDD';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        # Aggregation module - HPP
        'subset and conditional on MDD'
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph cluster_80 {
        rank = same; '(i*j*k)-th indirect damages to HPP' '(i*j*k)-th direct damages to HPP'
        }
        
        # [5] edges
        subgraph cluster_80 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'k-th HPP asset raster' '(i*j)-th hazard raster'} -> '(i*j*k)-th HPP exposure raster'
        {'HPP PAE' '(i*j*k)-th HPP exposure raster'} -> '(i*j*k)-th HPP damaged exposure raster'
        {'(i*j*k)-th HPP MDD' '(i*j*k)-th HPP damaged exposure raster'} -> '(i*j*k)-th direct damages to HPP'
        {'(i*j*k)-th HPP MDD' '(i*j*k)-th HPP damaged exposure raster' 'k-th HPP revenue raster'} -> 'subset and conditional on MDD' 
        'subset and conditional on MDD' -> '(i*j*k)-th indirect damages to HPP' 
        }

# ------------------------------

 # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module - road
        '(i*j)-th hazard raster';
        '(i*j)-th road exposure raster'; 
        '(i*j)-th road damaged exposure raster';
        '(i*j)-th mean road MDD';
        '(i*j)-th direct damages to road'; 
        '(i*j)-th indirect damages to road';
        'road asset raster';
        'road PAE';
        '(i*j)-th road MDD';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'data on (1) duration road closure and (2) customs revenues';        


        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph cluster_90 {
        rank = same; '(i*j)-th indirect damages to road' '(i*j)-th direct damages to road'
        }
        
        # [5] edges
        subgraph cluster_90 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'road asset raster' '(i*j)-th hazard raster'} -> '(i*j)-th road exposure raster' # 17b
        {'road PAE' '(i*j)-th road exposure raster'} -> '(i*j)-th road damaged exposure raster'  #17b
        {'(i*j)-th road MDD' '(i*j)-th road damaged exposure raster'} -> '(i*j)-th direct damages to road' #17b
        {'(i*j)-th road MDD'} -> '(i*j)-th mean road MDD' #17b
        {'(i*j)-th mean road MDD' 'data on (1) duration road closure and (2) customs revenues'} -> '(i*j)-th indirect damages to road' # 17b
        }


#---------------------
# [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module - settlement
        '(i*j)-th hazard raster'        
        '(i*j*k)-th settlement exposure raster';  
        '(i*j*k)-th settlement damaged exposure raster';
        '(i*j*k)-th direct damages to settlement'; 
        '(i*j)-th indirect damages to settlement';
        'k-th settlement asset raster';
        'settlement PAE';
        '(i*j)-th mean road MDD';
        '(i*j*k)-th settlement MDD'
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'data on road-related income';        

        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph cluster_100 {
        rank = same; '(i*j*k)-th direct damages to settlement' '(i*j)-th indirect damages to settlement';
        }
        
        # [5] edges
        subgraph cluster_100 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'k-th settlement asset raster' '(i*j)-th hazard raster'} -> '(i*j*k)-th settlement exposure raster' # 17b
        {'settlement PAE' '(i*j*k)-th settlement exposure raster'} -> '(i*j*k)-th settlement damaged exposure raster'  #17b
        {'(i*j*k)-th settlement MDD' '(i*j*k)-th settlement damaged exposure raster'} -> '(i*j*k)-th direct damages to settlement' #17b
        {'(i*j)-th mean road MDD' 'data on road-related income'} -> '(i*j)-th indirect damages to settlement' # 17b
        }
 
#------------------------------------------

# [1] intermediary data / output data
      node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
      ## Aggregation module - farmland
      '(i*j)-th hazard raster'        
      '(i*j)-th farmland exposure raster';  
      '(i*j)-th farmland damaged exposure raster';
      '(i*j)-th direct damages to farmland';
      'farmland asset raster';
      '(i*j)-th hazard raster';
      'farmland PAE';
      '(i*j)-th farmland MDD';
      
      # [3] operations                
      node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
      
      # [7] input data
      node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
      
      # [6] title names
      node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
      
      # [4] sort or separate
      subgraph cluster_110 {
      rank = same; '(i*j)-th direct damages to farmland'
      }
      
      # [5] edges
      subgraph cluster_110 {
      edge [color = grey, arrowhead = vee, arrowtail = none]
      {'farmland asset raster' '(i*j)-th hazard raster'} -> '(i*j)-th farmland exposure raster' 
      {'farmland PAE' '(i*j)-th farmland exposure raster'} -> '(i*j)-th farmland damaged exposure raster' 
      {'(i*j)-th farmland MDD' '(i*j)-th farmland damaged exposure raster'} -> '(i*j)-th direct damages to farmland'
      }
             
        }
        ")

name_1000

```

## Consolidated modules - hazard module and aggregation module (hazard rasters only)

```{r, results="asis"}

name_1100 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
#---------------------------------------

        # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, data preparation        
        'unfilled DEM raster';
        'polygon of watershed with outlet at Dolalghat';  
        'results of DEM validation';
        'DEM raster';
        'boolean river raster';
        'slope raster';
        'polygon of study area';
        'river reach ID raster';
        'river reach ID buffer raster';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, data preparation        
        'ArcGIS analysis'; 
        'elevation RMSE';
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, data preparation
        'SRTM 1 arc-sec rasters'; 'ASTER 1 arc-sec rasters';
        'GPS measurements';
        'polygon of Nepal by district';
        
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same;
        }
        
        # [5] edges
        subgraph cluster_20 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'SRTM 1 arc-sec rasters' 'ASTER 1 arc-sec rasters'} ->'unfilled DEM raster'
        'unfilled DEM raster' 
        }
        
        # [5] edges
        subgraph cluster_20 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        #1.5
        'unfilled DEM raster' -> 'ArcGIS analysis'
        'ArcGIS analysis' -> {'polygon of watershed with outlet at Dolalghat' 'DEM raster' 'boolean river raster' 'slope raster' 'river reach ID buffer raster'}
        {'polygon of watershed with outlet at Dolalghat' 'polygon of Nepal by district'} -> 'polygon of study area'
        }
        
        # [5] edges
        subgraph cluster_20 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'DEM raster' 'GPS measurements'} -> 'elevation RMSE' 
        'elevation RMSE' -> 'results of DEM validation'
        }
        
        # [5] edges
        subgraph cluster_20 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'river reach ID buffer raster' 'boolean river raster'} -> 'river reach ID raster'
        }
        
#------------------------------

 # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, flood raster
        'i-th flood raster';  
        'i-th initial water stages by river reach'; 
        'results of validation of initial water stages';
        'initial water stage raster'; 
        'DEM raster';
        'river reach ID raster'
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, flood raster
        'distribution fitting'; 
        'quantile derivation'; 
        'dependencies of initial water stages'; 
        '(if DHM data available)';
        '(if DHM data not available)'; 
        'RMSE of initial water stage' 'flood function';
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: Floods, flood raster
        'empirical 99%-quantile of water stage (1)'; 
        'empirical 99%-quantile of water stage (2)';
        'DHM data: water discharge and water stage';
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same; 
        }
        
        # [5] edges
        subgraph cluster_30 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        '(if DHM data available)' -> 'DHM data: water discharge and water stage'
        '(if DHM data not available)'-> 'empirical 99%-quantile of water stage (1)'
        {'DHM data: water discharge and water stage' 'empirical 99%-quantile of water stage (1)'}-> 'distribution fitting'
        'distribution fitting' -> 'quantile derivation'
        {'quantile derivation' 'dependencies of initial water stages'} -> 'i-th initial water stages by river reach'
        }
        
        # [5] edges 
        subgraph cluster_30 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'i-th initial water stages by river reach' 'empirical 99%-quantile of water stage (2)'} -> 'RMSE of initial water stage' -> 'results of validation of initial water stages'
        }
        
        # [5] edges
        subgraph cluster_30 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'river reach ID raster' 'i-th initial water stages by river reach'} -> 'initial water stage raster'
        {'initial water stage raster' 'DEM raster'} -> 'flood function' -> 'i-th flood raster'
        }

#------------------------------

    # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: raster of possible landslides
        'slope raster' 
        'boolean slope >30% raster'; 
        'orientation at flood curve raster'; 
        'rock weight raster'; 
        'angle at flood curve raster'; 
        'angle weight raster'; 
        'toe orientation raster'; 
        'toe weight raster' ;
        'average size of landslides'; 
        'j-th ratio of landslide count'; 
        'boolean river raster';
        'polygon riparian areas';
        'i-th possible toe raster'
        'i-th flood raster'
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'select flooded toes';
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Hazard module: raster of possible landslides
        'data on rocks and geology'; 
        'polygons of geological formations';  
        'data on weights given angle'; 
        'landslide history data';
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same; 
        }
        
        # [5] edges
        subgraph cluster_40 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'slope raster' -> 'boolean slope >30% raster'
        'boolean river raster' -> 'orientation at flood curve raster'
        {'boolean slope >30% raster' 'orientation at flood curve raster'}  -> 'toe orientation raster'
        }
        
        # [5] edges
        subgraph cluster_40 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'data on rocks and geology' 'polygons of geological formations'} -> 'rock weight raster'   
        {'boolean river raster' 'orientation at flood curve raster'} -> 'angle at flood curve raster' 
        {'angle at flood curve raster' 'data on weights given angle'} -> 'angle weight raster' 
        {'angle weight raster' 'rock weight raster'} -> 'toe weight raster' 
        }
        
        # [5] edges
        subgraph cluster_40 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'landslide history data' -> 'average size of landslides'
        'boolean river raster'  -> 'polygon riparian areas'
        {'landslide history data' 'polygon riparian areas'} -> 'j-th ratio of landslide count'
        }

        # [5] edges
        subgraph cluster_40 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'toe orientation raster' 'i-th flood raster'} -> 'select flooded toes' 
        'select flooded toes' -> 'i-th possible toe raster'
        }


#--------------------------------

         # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module: hazard rasters
        'i-th possible toe raster'; 
        '(i*j)-th actual landslide raster'; 
        'i-th flood raster'; 
        'j-th ratio of landslide count'; 
        'toe weight raster'; 
        'average size of landslides'; 
        '(i*j)-th hazard raster';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module: hazard rasters
        'build-landslide function';
        'join hazards';
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same; 
        }
        
        # [5] edges      
        subgraph cluster_70 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'j-th ratio of landslide count' 'i-th possible toe raster' 'toe weight raster' 'average size of landslides'} -> 'build-landslide function' 
        'build-landslide function' -> '(i*j)-th actual landslide raster'
        {'i-th flood raster''(i*j)-th actual landslide raster'} -> 'join hazards' 
        'join hazards' -> '(i*j)-th hazard raster' 
        }
             
        }
        ")

name_1100

```

## Consolidated modules - asset module and aggregation module (w/o hazard rasters)

```{r, results="asis"}

name_1200 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey, rankdir = LR]

#---------------------------------------


     # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Asset module: value rasters
        'k-th HPP asset raster' 
        'k-th HPP revenue raster' 
        'road asset raster' 
        'LULC raster' 
        'boolean settlement raster' 
        'boolean farmland raster' 
        'k-th settlement asset raster' 
        'farmland asset raster';
        'k-th points of HW and PH locations'
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Asset module: value rasters
        'polygons of HPPs lease areas' 
        'data on location of HW and PH' 
        'data on unit cost per MW' 
        'data on maximum revenue per MW' 
        'boolean road raster' 
        'data on unit cost per km' 
        'Sentinel data' 
        'data on unit cost and HH density' 
        'data on farm gate price and crop type';
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]

        # [4] sort or separate
        subgraph {
        rank = same; 
        }        
        

        # [5] edges
        subgraph cluster_50 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'polygons of HPPs lease areas' 'data on location of HW and PH'} -> 'k-th points of HW and PH locations'
        {'data on unit cost per MW'  'k-th points of HW and PH locations'} -> 'k-th HPP asset raster'
        }
        
        # [5] edges
        subgraph cluster_50 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'data on maximum revenue per MW' 'k-th points of HW and PH locations'} -> 'k-th HPP revenue raster'
        }
        
        # [5] edges
        subgraph cluster_50 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'data on unit cost per km' 'boolean road raster'} -> 'road asset raster'
        }
        
        # [5] edges
        subgraph cluster_50 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'Sentinel data' -> 'LULC raster'
        'LULC raster' -> 'boolean settlement raster'
        {'boolean settlement raster' 'data on unit cost and HH density'} -> 'k-th settlement asset raster'
        'k-th settlement asset raster'
        }
        
        # [5] edges
        subgraph cluster_50 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'LULC raster' -> 'boolean farmland raster' #15
        {'boolean farmland raster' 'data on farm gate price and crop type'} -> 'farmland asset raster'
        'farmland asset raster'
        }

#------------------------

  # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module: PAE and MDD
        'HPP PAE';
        'road PAE'; 
        'settlement PAE';
        'farmland PAE'; '(i*j*k)-th HPP MDD';
        '(i*j)-th road MDD';
        '(i*j*k)-th settlement MDD';
        '(i*j)-th farmland MDD';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module: PAE and MDD        
        'set deterministic PAE';
        'parameterise stochastic MDD';
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module: PAE and MDD        
        'asset valuation data';
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same; 
        }         
        
        # [5] edges
        subgraph cluster_60 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'asset valuation data'
        }
        
        # [5] edges
        subgraph cluster_60 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'asset valuation data' -> 'set deterministic PAE' 
        'set deterministic PAE' -> {'HPP PAE' 'road PAE' 'settlement PAE' 'farmland PAE'}
        }
        
        # [5] edges 
        subgraph cluster_60 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'asset valuation data' -> 'parameterise stochastic MDD'
        'parameterise stochastic MDD' -> {'(i*j*k)-th HPP MDD' '(i*j)-th road MDD' '(i*j*k)-th settlement MDD' '(i*j)-th farmland MDD'}
        }      

#---------------------

        # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module: hazard rasters
        '(i*j)-th hazard raster';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph {
        rank = same; '(i*j)-th hazard raster'
        }
        
        # [5] edges      
        subgraph cluster_70 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        '(i*j)-th hazard raster' 
        }
        
#------------------------------

 # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module - HPP
        '(i*j)-th hazard raster';
        'k-th HPP asset raster';
        '(i*j*k)-th HPP exposure raster';
        '(i*j*k)-th HPP damaged exposure raster'; 
        '(i*j*k)-th direct damages to HPP'; 
        '(i*j*k)-th indirect damages to HPP';
        'HPP PAE';
        'k-th HPP revenue raster';
        '(i*j*k)-th HPP MDD';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        # Aggregation module - HPP
        'subset and conditional on MDD'
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph cluster_80 {
        rank = same; '(i*j*k)-th indirect damages to HPP' '(i*j*k)-th direct damages to HPP'
        }
        
        # [5] edges
        subgraph cluster_80 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'k-th HPP asset raster' '(i*j)-th hazard raster'} -> '(i*j*k)-th HPP exposure raster'
        {'HPP PAE' '(i*j*k)-th HPP exposure raster'} -> '(i*j*k)-th HPP damaged exposure raster'
        {'(i*j*k)-th HPP MDD' '(i*j*k)-th HPP damaged exposure raster'} -> '(i*j*k)-th direct damages to HPP'
        {'(i*j*k)-th HPP MDD' '(i*j*k)-th HPP damaged exposure raster' 'k-th HPP revenue raster'} -> 'subset and conditional on MDD' 
        'subset and conditional on MDD' -> '(i*j*k)-th indirect damages to HPP' 
        }

# ------------------------------

 # [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module - road
        '(i*j)-th hazard raster';
        '(i*j)-th road exposure raster'; 
        '(i*j)-th road damaged exposure raster';
        '(i*j)-th mean road MDD';
        '(i*j)-th direct damages to road'; 
        '(i*j)-th indirect damages to road';
        'road asset raster';
        'road PAE';
        '(i*j)-th road MDD';
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'data on (1) duration road closure and (2) customs revenues';        


        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph cluster_90 {
        rank = same; '(i*j)-th indirect damages to road' '(i*j)-th direct damages to road'
        }
        
        # [5] edges
        subgraph cluster_90 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'road asset raster' '(i*j)-th hazard raster'} -> '(i*j)-th road exposure raster' # 17b
        {'road PAE' '(i*j)-th road exposure raster'} -> '(i*j)-th road damaged exposure raster'  #17b
        {'(i*j)-th road MDD' '(i*j)-th road damaged exposure raster'} -> '(i*j)-th direct damages to road' #17b
        {'(i*j)-th road MDD'} -> '(i*j)-th mean road MDD' #17b
        {'(i*j)-th mean road MDD' 'data on (1) duration road closure and (2) customs revenues'} -> '(i*j)-th indirect damages to road' # 17b
        }


#---------------------
# [1] intermediary data / output data
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        ## Aggregation module - settlement
        '(i*j)-th hazard raster'        
        '(i*j*k)-th settlement exposure raster';  
        '(i*j*k)-th settlement damaged exposure raster';
        '(i*j*k)-th direct damages to settlement'; 
        '(i*j)-th indirect damages to settlement';
        'k-th settlement asset raster';
        'settlement PAE';
        '(i*j)-th mean road MDD';
        '(i*j*k)-th settlement MDD'
        
        # [3] operations                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [7] input data
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'data on road-related income';        

        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        
        # [4] sort or separate
        subgraph cluster_100 {
        rank = same; '(i*j*k)-th direct damages to settlement' '(i*j)-th indirect damages to settlement';
        }
        
        # [5] edges
        subgraph cluster_100 {
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'k-th settlement asset raster' '(i*j)-th hazard raster'} -> '(i*j*k)-th settlement exposure raster' # 17b
        {'settlement PAE' '(i*j*k)-th settlement exposure raster'} -> '(i*j*k)-th settlement damaged exposure raster'  #17b
        {'(i*j*k)-th settlement MDD' '(i*j*k)-th settlement damaged exposure raster'} -> '(i*j*k)-th direct damages to settlement' #17b
        {'(i*j)-th mean road MDD' 'data on road-related income'} -> '(i*j)-th indirect damages to settlement' # 17b
        }
 
#------------------------------------------

# [1] intermediary data / output data
      node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
      ## Aggregation module - farmland
      '(i*j)-th hazard raster'        
      '(i*j)-th farmland exposure raster';  
      '(i*j)-th farmland damaged exposure raster';
      '(i*j)-th direct damages to farmland';
      'farmland asset raster';
      '(i*j)-th hazard raster';
      'farmland PAE';
      '(i*j)-th farmland MDD';
      
      # [3] operations                
      node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
      
      # [7] input data
      node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
      
      # [6] title names
      node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
      
      # [4] sort or separate
      subgraph cluster_110 {
      rank = same; '(i*j)-th direct damages to farmland'
      }
      
      # [5] edges
      subgraph cluster_110 {
      edge [color = grey, arrowhead = vee, arrowtail = none]
      {'farmland asset raster' '(i*j)-th hazard raster'} -> '(i*j)-th farmland exposure raster' 
      {'farmland PAE' '(i*j)-th farmland exposure raster'} -> '(i*j)-th farmland damaged exposure raster' 
      {'(i*j)-th farmland MDD' '(i*j)-th farmland damaged exposure raster'} -> '(i*j)-th direct damages to farmland'
      }
             
        }
        ")

name_1200

```

# Methods: All papers and thesis

## Overview methodology
```{r}
name_000 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] data not present in previous stages / response in general
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'Qualitative primary data'; 
        'Quantitative primary data';
        'Qualitative secondary data'; 
        'Quantitative secondary data'        
        
         # [2] data present in next stage / final output
        node [color = orange, shape = triangle, style = filled, fillcolor= OldLace, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'Results'        
        
        # [3] operations  / conditions or questions                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'Data collection, using: '
        'Interviews'
        'Literature review'
        'Other sources'
        'Model design, including: '
        'Characteristics of hazards underlying flood risk in Nepal'
        'Variables quantifying flood risk'
        'Modelling'
        
        # [7] data from previous stages  / response in model
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        'Methodology'
   
        # [4] sort or separate
        subgraph {
        rank = same;
        }

        # [5] edges      
        subgraph cluster_1 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'Methodology'
        }
        
        # [5] edges      
        subgraph cluster_2 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'Methodology' -> 'Data collection, using: '        
        'Data collection, using: ' -> {'Interviews' 'Literature review' 'Other sources'}
        'Interviews' -> {'Qualitative primary data' 'Quantitative primary data'}
        'Literature review' -> {'Qualitative secondary data' 'Quantitative secondary data'}
        'Other sources' -> 'Quantitative secondary data'
        }
        
        # [5] edges      
        subgraph cluster_3 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'Quantitative primary data' 'Qualitative primary data' 'Qualitative secondary data' 'Quantitative secondary data'} -> 'Model design, including: '
'Model design, including: ' -> {'Characteristics of hazards underlying flood risk in Nepal' 'Variables quantifying flood risk'}
        }        
        
        # [5] edges      
        subgraph cluster_4 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'Characteristics of hazards underlying flood risk in Nepal' 'Variables quantifying flood risk'} -> 'Modelling'
        } 
        
        # [5] edges      
        subgraph cluster_4 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'Modelling' -> 'Results'
        } 
        
        }
        
        ")

name_000

#WRITE_AS_SVG(name_000,"000.svg")

```


## Characteristics of hazards underlying flood risk
```{r}

name_010 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] data not present in previous stages / response in general
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
         # [2] data present in next stage / final output
        node [color = orange, shape = triangle, style = filled, fillcolor= OldLace, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'Flood-related hazards in model'        
        
        # [3] operations  / conditions or questions                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'Triggering mechanisms?'; 
        'Surrounding area?'; 
        'Timing?'; 
        'Hazards cascading from floods?'

        # [7] data from previous stages  / response in model
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'Rainfall, GLOF, LDOF, sediment accumulation'; 'Riperian areas'; 'Flash floods all year round'; 'Flood-induced landslides'         

        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        'Characteristics of hazards underlying flood risk'
   
        # [4] sort or separate
        subgraph {
        rank = same;
        }
    
        # [5] edges      
        subgraph cluster { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'Characteristics of hazards underlying flood risk' -> {'Triggering mechanisms?'; 'Surrounding area?'; 'Timing?'; 'Hazards cascading from floods?'}
        'Triggering mechanisms?' -> 'Rainfall, GLOF, LDOF, sediment accumulation'
        'Surrounding area?' -> 'Riperian areas'
        'Timing?' -> 'Flash floods all year round'
        'Hazards cascading from floods?' -> 'Flood-induced landslides'
        {'Rainfall, GLOF, LDOF, sediment accumulation'; 'Riperian areas'; 'Flash floods all year round'; 'Flood-induced landslides'} -> 'Flood-related hazards in model'
        }
        
        }
        
        ")

name_010
#WRITE_AS_SVG(name_010,"010.svg")
```

## Supporting elements to livelihoods

```{r}
name_020 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] data not present in previous stages / response in general
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'Elements supporting livelihoods' 
        'Vulnerable supporting elements are assets'
        'Vulnerable supporting elements are not assets'
        
         # [2] data present in next stage / final output
        node [color = orange, shape = triangle, style = filled, fillcolor= OldLace, fontname = Helvetica, fixedsize = false, fontsize = 14]
        
        # [3] operations  / conditions or questions                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'Whose livelihoods?'
        'Which supporting elements?'
        'If elements vulnerable to flood risk'
        'Can be valued in monetary terms and have a physical existence?'
        
        # [7] data from previous stages  / response in model
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'Flood-related hazards in model'        

        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        'Variables quantifying flood risk'
        
        # [4] sort or separate
        subgraph {
        rank = same; 'Flood-related hazards in model' 'If elements vulnerable to flood risk'
        }

         # [5] edges      
        subgraph cluster_00 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'Variables quantifying flood risk'
        }

        # [5] edges      
        subgraph cluster_01 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
'Variables quantifying flood risk' ->   {'Whose livelihoods?' 'Which supporting elements?'}      
{'Whose livelihoods?' 'Which supporting elements?'} -> 'Elements supporting livelihoods' 
        'Elements supporting livelihoods' -> 'If elements vulnerable to flood risk'
        }

        # [5] edges      
        subgraph cluster_02 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'Flood-related hazards in model' -> 'If elements vulnerable to flood risk'
        'If elements vulnerable to flood risk' -> 'Can be valued in monetary terms and have a physical existence?'
        'Can be valued in monetary terms and have a physical existence?' -> {'Vulnerable supporting elements are assets' 'Vulnerable supporting elements are not assets'}
        }

        }
        
        ")

name_020

#WRITE_AS_SVG(name_020,"020.svg")

```

# Methods by paper

## LULC paper: Methods

```{r}


name_400 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] data not present in previous stages / response in general
        node [color = gray, shape = oval, style = filled, fillcolor= gray, fontname = Helvetica, fixedsize = false, fontsize = 14, fontcolor = white]
        'Sentinel-2 Level-1A'
        'Ground control points (GCPs)'
        'Topographical thresholds'
        
        # [2] data present in next stage / final output
        node [color = gray, shape = triangle, style = filled, fillcolor= gray, fontname = Helvetica, fixedsize = false, fontsize = 14, fontcolor = white]
        
        # [3] operations  / conditions or questions                
        node [color = gray, shape = diamond, style = filled, fillcolor= gray, fontname = Helvetica, fixedsize = false, fontsize = 14, fontcolor = white]
        
        # [7] data from previous stages  / response in model
        node [color = gray, shape = box, style = filled, fillcolor= gray, fontname = Helvetica, fixedsize = false, fontsize = 14, fontcolor = white]
        'Cloud correction'
        'Median for each band'
        'Training GCPs'
        'Classification'
        'Classification and Regression Tree'
        'Random Forest'
        'Max Entropy'
        'Validation GCPs'
        'Validation'
        'Confusion matrices (n = 3)'
        'Confusion matrices by topographical category (n = 18)'
        'Kappa coefficient and Kappa standard deviation'
        'Producer, user, and overall accuracy'
        'Selection of map of highest accuracy'
        'Producer and user accuracy'
        'General linear models'
        'Variables associated with producer and user accuracy'
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= gray, fontname = Helvetica, fixedsize = false, fontsize = 20, fontcolor = white]
        
        # [4] sort or separate
        subgraph {
        rank = same; 
        }
        
        # [5] edges      
        subgraph cluster1 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'Sentinel-2 Level-1A'                     -> 'Cloud correction'
        'Cloud correction'                        -> 'Median for each band' 
        'Ground control points (GCPs)'                                    -> {'Training GCPs' 'Validation GCPs'}
        {'Median for each band' 'Training GCPs'}  -> 'Classification'
        'Classification'                          -> {'Classification and Regression Tree''Random Forest''Max Entropy'}
        {'Classification and Regression Tree''Random Forest' 'Max Entropy' 'Validation GCPs'}  -> {Validation}
        
        
        }
        
        # [5] edges      
        subgraph cluster2 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'Validation'                              -> {'Confusion matrices (n = 3)' 'Confusion matrices by topographical category (n = 18)'}        
        'Confusion matrices (n = 3)'              -> {'Kappa coefficient and Kappa standard deviation' 'Producer, user, and overall accuracy'}
        {'Kappa coefficient and Kappa standard deviation' 'Producer, user, and overall accuracy'} -> 'Selection of map of highest accuracy'
        {'Confusion matrices by topographical category (n = 18)''Topographical thresholds'} -> 'Producer and user accuracy'
        'Producer and user accuracy'              -> 'General linear models'
        'General linear models'                   -> 'Variables associated with producer and user accuracy'
        }
        
        }
        
        ")

name_400

#WRITE_AS_SVG(name_400, "to LULC paper.svg")
```

## Vulnerability paper: Supporting elements to livelihoods vulnerable to flood risk
```{r}

name_300 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] data not present in previous stages / response in general
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'Vulnerable supporting elements are assets'
        'Vulnerable supporting elements are not assets'        
        
         # [2] data present in next stage / final output
        node [color = orange, shape = triangle, style = filled, fillcolor= OldLace, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'Area size of farmland'
        'Area size of settlement'
        'Number of households'
        'Hotspots of flood risk'        
        
        # [3] operations  / conditions or questions                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'Which elements are considered in model?' 

        # [7] data from previous stages  / response in model
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'Farmland'
        'Settlement'
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
        'Supporting elements to livelihoods vulnerable to flood risk'
        
        # [4] sort or separate
        subgraph {
        rank = same;
        }

      # [5] edges      
        subgraph cluster_01 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'Supporting elements to livelihoods vulnerable to flood risk'
        }
        
        # [5] edges      
        subgraph cluster_02 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'Supporting elements to livelihoods vulnerable to flood risk' -> {'Vulnerable supporting elements are assets'  'Vulnerable supporting elements are not assets'}
        {'Vulnerable supporting elements are assets'  'Vulnerable supporting elements are not assets'} ->  'Which elements are considered in model?' 
        }

        # [5] edges      
        subgraph cluster_03 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'Which elements are considered in model?' -> {'Farmland' 'Settlement'}
        'Farmland' -> 'Area size of farmland'
        'Settlement' -> {'Area size of settlement' 'Number of households'}
        {'Area size of farmland''Area size of settlement'} -> 'Hotspots of flood risk'
        }
        
        }
        
        ")

name_300
#WRITE_AS_SVG(name_300,"300.svg")
```

## Economic damages paper: Economic damages to elements supporting livelihoods

```{r}
name_200 <- 
  grViz(" digraph {
        graph [overlap = true, fontsize = 14, color= grey]
        
        # [1] data not present in previous stages / response in general
        node [color = red, shape = box, style = filled, fillcolor= mistyrose, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'Vulnerable supporting elements are assets'
        'Vulnerable supporting elements are not assets'
        'Direct tangible consequences (direct damages)'
        'Indirect tangible consequences (indirect damages)'
        'Direct intangible consequences'
        'Indirect intangible consequences'
        
        
        # [2] data present in next stage / final output
        node [color = orange, shape = triangle, style = filled, fillcolor= OldLace, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'Economic damages'
       
        
        # [3] operations  / conditions or questions                
        node [color = green, shape = diamond, style = filled, fillcolor= palegreen, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'If affected by flood-related hazards' 
        'Which elements considered in model?'
        'Which considered in model?'

        # [7] data from previous stages  / response in model
        node [color = blue, shape = oval, style = filled, fillcolor= lightcyan, fontname = Helvetica, fixedsize = false, fontsize = 14]
        'Direct damages to: HPP, road, settlement, farmland'
        'Indirect damages for: HPP, customs, local population'
        'Flood-related hazards in model'
        
        # [6] title names
        node [shape = plaintext, style = filled, fillcolor= white, fontname = Helvetica, fixedsize = false, fontsize = 20]
'Economic damages to elements supporting livelihoods'        

        # [4] sort or separate
        subgraph {
        rank = same; 'Flood-related hazards in model'; 'If affected by flood-related hazards'
        }

        # [5] edges      
        subgraph cluster_01 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'Economic damages to elements supporting livelihoods'
        }

        
        # [5] edges      
        subgraph cluster_02 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        'Economic damages to elements supporting livelihoods' -> {'Vulnerable supporting elements are assets' 'Vulnerable supporting elements are not assets'}
        {'Vulnerable supporting elements are assets' 'Vulnerable supporting elements are not assets'} -> 'Which elements considered in model?'
        {'Which elements considered in model?' 'Flood-related hazards in model'} -> 'If affected by flood-related hazards'
        }

        # [5] edges      
        subgraph cluster_03 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'If affected by flood-related hazards'} -> {'Direct tangible consequences (direct damages)' 'Indirect tangible consequences (indirect damages)' 'Direct intangible consequences' 'Indirect intangible consequences'}
        {'Direct tangible consequences (direct damages)' 'Indirect tangible consequences (indirect damages)''Direct intangible consequences' 'Indirect intangible consequences'} -> 'Which considered in model?'
        }

        # [5] edges      
        subgraph cluster_04 { 
        edge [color = grey, arrowhead = vee, arrowtail = none]
        {'Which considered in model?'} -> 'Direct damages to: HPP, road, settlement, farmland'
        {'Which considered in model?'} -> 'Indirect damages for: HPP, customs, local population'
        {'Direct damages to: HPP, road, settlement, farmland' 'Indirect damages for: HPP, customs, local population'} -> 'Economic damages'
        }

        }
        
        ")

name_200

#WRITE_AS_SVG(name_200,"nice.svg")

```

